The title

### 2022-10-31 paper/manuscript.Rmd
update results (analysis, floating points)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

author: 
  - name          : "Atsuko Tominaga"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Quellenstraße 51, 1100 Vienna, Austria"
    email         : "tominaga_atsuko@phd.ceu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Günther Knoblich"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Natalie Sebanz"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

@@

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

@@

classoption       : "man"
output            : papaja::apa6_word
---

```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"): require("papaja")}
if (!require("here")) {install.packages("here"): require("here")}
if (!require("magick")) {install.packages("magick"): require("magick")}
library(ggsci)
```

@@

```{r methods, include = FALSE}
source(here("analysis/demographics", "questionnaire.R"), chdir = TRUE)
source(here("analysis/preprocessor", "filtering.R"), chdir = TRUE)
```

@@

```{r results-1, include = FALSE}
source(here("analysis", "baseline.R"), chdir = TRUE)
```

@@

Neither main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* = `r ioi_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* = `r ioi_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* = `r ioi_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`). Therefore, participants did not change the tempo depending on the types of the recordings (*Fig \ref{fig:ioi-1}*).

@@

There was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* = `r leg_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* = `r leg_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* = `r leg_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`). Participants produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left).

@@

There was a significant main effect of Articulation (*F*(`r sta_all_aov$anova_table[1,1]`, `r sta_all_aov$anova_table[1,2]`) = `r sta_all_aov$anova_table[1,4]`, *p* = `r sta_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r sta_all_aov$anova_table[2,1]`, `r sta_all_aov$anova_table[2,2]`) = `r sta_all_aov$anova_table[2,4]`, *p* = `r sta_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r sta_all_aov$anova_table[3,1]`, `r sta_all_aov$anova_table[3,2]`) = `r sta_all_aov$anova_table[3,4]`, *p* = `r sta_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[3,5])`). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, right).

@@

Neither main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* = `r for_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* = `r for_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* = `r for_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`). Participants did not change performances in terms of dynamics (loudness) depending on the types of the recordings (*Fig \ref{fig:vel-1}*, left).

@@

There was a significant main effect of Articulation (*F*(`r pia_all_aov$anova_table[1,1]`, `r pia_all_aov$anova_table[1,2]`) = `r pia_all_aov$anova_table[1,4]`, *p* = `r pia_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r pia_all_aov$anova_table[2,1]`, `r pia_all_aov$anova_table[2,2]`) = `r pia_all_aov$anova_table[2,4]`, *p* = `r pia_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r pia_all_aov$anova_table[3,1]`, `r pia_all_aov$anova_table[3,2]`) = `r pia_all_aov$anova_table[3,4]`, *p* = `r pia_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[3,5])`). Participants produced softer piano when listening to the recordings where articulation was implemented (*Fig \ref{fig:vel-1}*, right).

@@

Neither main effect of Articulation (*F*(`r ftop_all_aov$anova_table[1,1]`, `r ftop_all_aov$anova_table[1,2]`) = `r ftop_all_aov$anova_table[1,4]`, *p* = `r ftop_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ftop_all_aov$anova_table[2,1]`, `r ftop_all_aov$anova_table[2,2]`) = `r ftop_all_aov$anova_table[2,4]`, *p* = `r ftop_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ftop_all_aov$anova_table[3,1]`, `r ftop_all_aov$anova_table[3,2]`) = `r ftop_all_aov$anova_table[3,4]`, *p* = `r ftop_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[3,5])`).

@@

Neither main effect of Articulation (*F*(`r ptof_all_aov$anova_table[1,1]`, `r ptof_all_aov$anova_table[1,2]`) = `r ptof_all_aov$anova_table[1,4]`, *p* = `r ptof_all_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ptof_all_aov$anova_table[2,1]`, `r ptof_all_aov$anova_table[2,2]`) = `r ptof_all_aov$anova_table[2,4]`, *p* = `r ptof_all_aov$anova_table[2,6]`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ptof_all_aov$anova_table[3,1]`, `r ptof_all_aov$anova_table[3,2]`) = `r ptof_all_aov$anova_table[3,4]`, *p* = `r ptof_all_aov$anova_table[3,6]`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[3,5])`).

@@

There was no significant main effect of Category (*F*(`r ioi_ca_par_aov$anova_table[1,1]`, `r ioi_ca_par_aov$anova_table[1,2]`) = `r ioi_ca_par_aov$anova_table[1,4]`, *p* = `r ioi_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ioi_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected), suggesting that participants kept the same tempo regardless of whether they had an intention to teach (*Fig \ref{fig:ioi-2}*).

@@

There was a significant main effect of Category (*F*(`r leg_ca_par_aov$anova_table[1,1]`, `r leg_ca_par_aov$anova_table[1,2]`) = `r leg_ca_par_aov$anova_table[1,4]`, *p* = `r leg_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', leg_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: *p* < .001 , baseline and dynamics-only: *p* = .008), suggesting that participants produced longer legato when they had an intention to teach (*Fig \ref{fig:kot-2}*, left).

@@

There was no significant main effect of Category (*F*(`r sta_ca_par_aov$anova_table[1,1]`, `r sta_ca_par_aov$anova_table[1,2]`) = `r sta_ca_par_aov$anova_table[1,4]`, *p* = `r sta_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', sta_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected), suggesting that participants did not play staccato differently depending on whether they had an intention to teach (*Fig \ref{fig:kot-2}*, right).

@@

There was no significant main effect of Category (*F*(`r for_ca_par_aov$anova_table[1,1]`, `r for_ca_par_aov$anova_table[1,2]`) = `r for_ca_par_aov$anova_table[1,4]`, *p* = `r for_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', for_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected), suggesting that participants did not play forte differently depending on whether they had an intention to teach (*Fig \ref{fig:vel-2}*, left).

@@

There was a significant main effect of Category (*F*(`r pia_ca_par_aov$anova_table[1,1]`, `r pia_ca_par_aov$anova_table[1,2]`) = `r pia_ca_par_aov$anova_table[1,4]`, *p* = `r pia_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', pia_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: *p* = .05 , baseline and articulation-only: *p* = .03), suggesting that participants produced softer piano when they had an intention to teach (*Fig \ref{fig:vel-2}*, right).

@@

There was no significant main effect of Category (*F*(`r ftop_ca_par_aov$anova_table[1,1]`, `r ftop_ca_par_aov$anova_table[1,2]`) = `r ftop_ca_par_aov$anova_table[1,4]`, *p* = `r ftop_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ftop_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected).

@@

There was no significant main effect of Category (*F*(`r ptof_ca_par_aov$anova_table[1,1]`, `r ptof_ca_par_aov$anova_table[1,2]`) = `r ptof_ca_par_aov$anova_table[1,4]`, *p* = `r ptof_ca_par_aov$anova_table[1,6]`, $\eta_G^2$ = `r sprintf('%.3f', ptof_ca_par_aov$anova_table[1,5])`; Greenhouse–Geisser corrected).

@@

```{r results-2, include = FALSE}
source(here("analysis", "onlyfirst.R"), chdir = TRUE)
```

@@

>>>>

author: 
  - name          : "Atsuko Tominaga"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Quellenstraße 51, 1100 Vienna, Austria"
    email         : "tominaga_atsuko@phd.ceu.edu"
    # role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
    #   - "Conceptualization"
    #   - "Writing - Original Draft Preparation"
    #   - "Writing - Review & Editing"
  - name          : "Günther Knoblich"
    affiliation   : "1"
    # role:
    #   - "Writing - Review & Editing"
    #   - "Supervision"
  - name          : "Natalie Sebanz"
    affiliation   : "1"
    # role:
    #   - "Writing - Review & Editing"
    #   - "Supervision"

@@

# authornote: |

abstract: |
  AAA

@@

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"): require("papaja")}
if (!require("here")) {install.packages("here"): require("here")}
if (!require("magick")) {install.packages("magick"): require("magick")}
if (!require("ggsci")) {install.packages("ggsci"): require("ggsci")}
```

@@

```{r methods, include = FALSE} 
here::i_am("README.md")
source(here("analysis/demographics" , "questionnaire.R"), chdir = TRUE)
source(here("analysis/preprocessor", "filtering.R"), chdir = TRUE)
```

@@

```{r results-1, include = FALSE}
here::i_am("README.md")
source(here("analysis", "baseline.R"), chdir = TRUE)
```

@@

Neither main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* `r if(ioi_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* `r if(ioi_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* `r if(ioi_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`). Therefore, participants did not change the tempo depending on the types of the recordings (*Fig \ref{fig:ioi-1}*).

@@

There was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* `r if(leg_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* `r if(leg_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* `r if(leg_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`). Participants produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left).

@@

There was a significant main effect of Articulation (*F*(`r sta_all_aov$anova_table[1,1]`, `r sta_all_aov$anova_table[1,2]`) = `r sta_all_aov$anova_table[1,4]`, *p* `r if(sta_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r sta_all_aov$anova_table[2,1]`, `r sta_all_aov$anova_table[2,2]`) = `r sta_all_aov$anova_table[2,4]`, *p* `r if(sta_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', sta_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r sta_all_aov$anova_table[3,1]`, `r sta_all_aov$anova_table[3,2]`) = `r sta_all_aov$anova_table[3,4]`, *p* `r if(sta_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[3,5])`). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, right).

@@

Neither main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* `r if(for_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', for_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', for_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* `r if(for_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* `r if(for_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`). Participants did not change performances in terms of dynamics (loudness) depending on the types of the recordings (*Fig \ref{fig:vel-1}*, left).

@@

There was a significant main effect of Articulation (*F*(`r pia_all_aov$anova_table[1,1]`, `r pia_all_aov$anova_table[1,2]`) = `r pia_all_aov$anova_table[1,4]`, *p* `r if(pia_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r pia_all_aov$anova_table[2,1]`, `r pia_all_aov$anova_table[2,2]`) = `r pia_all_aov$anova_table[2,4]`, *p* `r if(pia_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[2,5])`) or interaction between Articulation and Dynamics (*F*(`r pia_all_aov$anova_table[3,1]`, `r pia_all_aov$anova_table[3,2]`) = `r pia_all_aov$anova_table[3,4]`, *p* `r if(pia_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[3,5])`). Participants produced softer piano when listening to the recordings where articulation was implemented (*Fig \ref{fig:vel-1}*, right).

@@

Neither main effect of Articulation (*F*(`r ftop_all_aov$anova_table[1,1]`, `r ftop_all_aov$anova_table[1,2]`) = `r ftop_all_aov$anova_table[1,4]`, *p* `r if(ftop_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ftop_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ftop_all_aov$anova_table[2,1]`, `r ftop_all_aov$anova_table[2,2]`) = `r ftop_all_aov$anova_table[2,4]`, *p* `r if(ftop_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ftop_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ftop_all_aov$anova_table[3,1]`, `r ftop_all_aov$anova_table[3,2]`) = `r ftop_all_aov$anova_table[3,4]`, *p* `r if(ftop_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ftop_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_all_aov$anova_table[3,5])`).

@@

Neither main effect of Articulation (*F*(`r ptof_all_aov$anova_table[1,1]`, `r ptof_all_aov$anova_table[1,2]`) = `r ptof_all_aov$anova_table[1,4]`, *p* `r if(ptof_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ptof_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[1,5])`) or Dynamics (*F*(`r ptof_all_aov$anova_table[2,1]`, `r ptof_all_aov$anova_table[2,2]`) = `r ptof_all_aov$anova_table[2,4]`, *p* `r if(ptof_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ptof_all_aov$anova_table[3,1]`, `r ptof_all_aov$anova_table[3,2]`) = `r ptof_all_aov$anova_table[3,4]`, *p* `r if(ptof_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_all_aov$anova_table[3,5])`).

@@

There was no significant main effect of Category (*F*(`r ioi_ca_par_aov$anova_table[1,1]`, `r ioi_ca_par_aov$anova_table[1,2]`) = `r ioi_ca_par_aov$anova_table[1,4]`, *p* `r if(ioi_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected), suggesting that participants kept the same tempo regardless of whether they had an intention to teach (*Fig \ref{fig:ioi-2}*).

@@

There was a significant main effect of Category (*F*(`r leg_ca_par_aov$anova_table[1,1]`, `r leg_ca_par_aov$anova_table[1,2]`) = `r leg_ca_par_aov$anova_table[1,4]`, *p* `r if(leg_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: *p* < .001 , baseline and dynamics-only: *p* .008), suggesting that participants produced longer legato when they had an intention to teach (*Fig \ref{fig:kot-2}*, left).

@@

There was no significant main effect of Category (*F*(`r sta_ca_par_aov$anova_table[1,1]`, `r sta_ca_par_aov$anova_table[1,2]`) = `r sta_ca_par_aov$anova_table[1,4]`, *p* `r if(sta_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', sta_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected), suggesting that participants did not play staccato differently depending on whether they had an intention to teach (*Fig \ref{fig:kot-2}*, right).

@@

There was no significant main effect of Category (*F*(`r for_ca_par_aov$anova_table[1,1]`, `r for_ca_par_aov$anova_table[1,2]`) = `r for_ca_par_aov$anova_table[1,4]`, *p* `r if(for_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected), suggesting that participants did not play forte differently depending on whether they had an intention to teach (*Fig \ref{fig:vel-2}*, left).

@@

There was a significant main effect of Category (*F*(`r pia_ca_par_aov$anova_table[1,1]`, `r pia_ca_par_aov$anova_table[1,2]`) = `r pia_ca_par_aov$anova_table[1,4]`, *p* `r if(pia_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', pia_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: *p* .05 , baseline and articulation-only: *p* .03), suggesting that participants produced softer piano when they had an intention to teach (*Fig \ref{fig:vel-2}*, right).

@@

There was no significant main effect of Category (*F*(`r ftop_ca_par_aov$anova_table[1,1]`, `r ftop_ca_par_aov$anova_table[1,2]`) = `r ftop_ca_par_aov$anova_table[1,4]`, *p* `r if(ftop_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ftop_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ftop_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected).

@@

There was no significant main effect of Category (*F*(`r ptof_ca_par_aov$anova_table[1,1]`, `r ptof_ca_par_aov$anova_table[1,2]`) = `r ptof_ca_par_aov$anova_table[1,4]`, *p* `r if(ptof_ca_par_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ptof_ca_par_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ptof_ca_par_aov$anova_table[1,5])`; Greenhouse-Geisser corrected).

@@

@@

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We manipulated the implementation of articulation and dynamics in the piece to create four types of artificial recordings. These recordings were supposed to be the reflection of students' skill levels. In one quarter of the recordings, both articulation and dynamics were implemented
[SUMMARY].
We found that 
Limitation
